### 2018-05-26 background.tex
Change the loop name N, K, M to jj, kk, ii

As stated in Section~\ref{sec:intro}, a GEMM implementation
is made up by a kernel routine and an overall workload-partitioning strategy.
In Figure~\ref{fig:gemm}, GEBP serves as the kernel routine,
and the overall workload-partitioning strategy is defined by the three outer loops at layers 1 -- 3.
Developers can decide how to partition the workload by choosing
tile factors $M_c$, $N_c$ and $K_c$,
and how to schedule GEBP tasks by interchanging loop orders at layers 1 - 3.
Either the N loop at layer 1 or the M loop at layer 3, or 
both,
can be parallelized in a multi-threaded context.
Specifically, the implementation in Figure~\ref{fig:gemm}
chooses an NKM loop order and parallelizes the M loop at layer 3.
Different threads work on different parts of $A_1$
and share the same $B_1$.

As a result, there are multiple $A_2$ instances (one per thread)
and a single $B_2$ instance (shared by all threads).
To understand how the loop at layer 3 is parallelized on the 4-core processor, 
Figure.~\ref{fig:workload} shows the data accessing patterns of a single thread $T_1$.
While all color shaded submatrices are accessed by $T_1$,
only the z-curve masked submatrices (a subset of color shaded ones)
are packed by the thread.
In other words, each thread packs its own $A_2$ instance and  all the threads collaboratively pack the unique $B_2$ instance.
%% We will use the OpenBLAS GEMM implementation in Figure.~\ref{fig:gemm}
%% in discussion and evaluation throughout the paper.

>>>>

As stated in Section~\ref{sec:intro}, a GEMM implementation
is made up by a kernel routine and an overall workload-partitioning strategy.
In Figure~\ref{fig:gemm}, GEBP serves as the kernel routine,
and the overall workload-partitioning strategy is defined by the three outer loops at layers 1 -- 3.
Developers can decide how to partition the workload by choosing
tile factors $M_c$, $N_c$ and $K_c$,
and how to schedule GEBP tasks by interchanging loop orders at layers 1 - 3.
Either the $jj$ loop at layer 1 or the $ii$ loop at layer 3, or both,
can be parallelized in a multi-threaded context.
Specifically, the implementation in Figure~\ref{fig:gemm}
chooses an $jj\textrm{-}kk\textrm{-}ii$ loop order
and parallelizes the $ii$ loop at layer 3.
Different threads work on different parts of $A_1$
and share the same $B_1$.

As a result, there are multiple $A_2$ instances (one per thread)
and a single $B_2$ instance (shared by all threads).
To understand how the $ii$ loop at layer 3 is parallelized on the 4-core processor, 
Figure.~\ref{fig:workload} shows the data accessing patterns
of a single thread $T_1$.
While all color shaded submatrices are accessed by $T_1$,
only the z-curve masked submatrices (a subset of color shaded ones)
are packed by the thread.
In other words, each thread packs its own $A_2$ instance and  all the threads collaboratively pack the unique $B_2$ instance.
%% We will use the OpenBLAS GEMM implementation in Figure.~\ref{fig:gemm}
%% in discussion and evaluation throughout the paper.
